---
title: "Tidy Tuesday Week 32"
author: "Insights & Analytics"
format: html
editor: source
---

## Ferris Wheels 
The goal of ferriswheels is to provide a fun harmless little data set to play with

## Libaries

We will be using `Tidyverse`, `DataExplorer` and `TidyQuant`

```{r}
#| echo: false
#| warning: false
library(tidyverse)
library(DataExplorer)
library(lubridate)
library(tidyquant)
library(gt)
library(gtExtras)
```

## Data Analysis

```{r}
#| echo: false
wheels <- read_rds("../00_data/2022/week-32_wheels.rds")

wheels %>% glimpse()
```

Plot the missing values in each variable(column) of the dataset
```{r}
#| echo: false
#| label: missing-value in each column
#| fig-cap: Percentage of missing values in each column
plot_missing(wheels)
```

Delete Columns with majority of missing data and select initial columns for initial analysis 
```{r}
#| echo: false
wheels_tbl <- wheels %>% select(-c("closed","vip_area","turns","diameter","design_manufacturer")) %>%
  select(name,country, height,opened,status) %>% 
  mutate(country = as.factor(country))

wheels_tbl
```

## Plots 
### Plot by Height 
```{r}
#| echo: false
#| label: fig- Wheels by Height
#| fig-cap: 20 Tallest Ferris Wheels
#| fig-height: 8
wheels_tbl %>%
  arrange(desc(height)) %>% mutate(name = as_factor(name) %>% fct_rev()) %>% 
  slice(1:20) %>% 
  mutate(lab_1 = str_glue("{name}, {country},{year(opened)}")) %>% 
  ggplot(aes(name,height)) + 
  geom_col(fill = "#2c3e50") + 
  coord_flip()+ 
  geom_label(mapping = aes(label = lab_1),hjust = 1)  + theme_tq() +
  theme(axis.title.y =element_blank(),
        axis.text.y  =element_blank(),
        axis.ticks.y =element_blank()) + 
  labs(
    title = "Top 20 Ferris Wheels, by Height",
    caption = "Data : Tidy Tuesday \n @Emil_Hvitfeldt"
  )
```
### Summary Table, Country
```{r}
#| echo: false
#| label: table Summary
wheels_tbl %>% 
  group_by(country) %>% 
  summarise(count = n(),
            height  = list(height)) %>% 
  arrange(desc(count)) %>% gt() %>% 
  gtExtras::gt_plt_dist(column = "height",type = "histogram", fill_color = "red") %>% 
  gt_theme_nytimes() %>%
  tab_header(
    title = "Ferris Wheels Summary, by Country",
    subtitle = "Tidy Tuesday, Week 32"
  )
```

